Verifying Demonstrations

### 2017-10-04 protocol.tex
Splits temporal eligibility in protocol in two parts

Next we need to consider the protesters' identifiers to prevent Sybil attacks.
\Textcite{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another scheme that makes it non-interactive, e.g.\ by 
  \Textcite{Psignatures}, see issue \#27.
}.
Alice has a \ac{PRF} key \(k\) and a blind signature on \(k\) included in her 
national identity-card (by assumption).
She will use \(k\) to compute \(pid\gets PRF_k(id)\), which is her anonymous 
identity during the protest.
She must also provide \iac{NIZK} proof that \(pid = PRF_k(id)\) and that she 
knows a signature by the identity authority on \(k\).
Thus \(pid\) will be used as the unique identifier in the proof shares and the 
\ac{NIZK} proof will prove the eligibility of \(pid\).

\subsubsection{Temporal eligibility}

Given the properties of the storage (in \cref{StorageProperties}), 
\cref{CreatedBeforeEnd} is straight-forward: Alice and Bob simply commit their 
proofs to the blockchain as soon as possible after they have participated in the 
protest.
Thus we can infer that a proof (or proof share) was created at the latest when 
it was committed.
For \cref{CreatedAfterStart}, Alice and Bob must include the hash value of an 
existing block in the blockchain (\(t_s\) in \cref{ProofFig}).
Then it is clear that the proof must have been created after that block (since 
predicting such a value is hard).

@@

>>>>

Next we need to consider the protesters' identifiers to prevent Sybil attacks.
\Textcite{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another scheme that makes it non-interactive, e.g.\ by 
  \Textcite{Psignatures}, see issue \#27.
}.
Alice has a \ac{PRF} key \(k\) and a blind signature on \(k\) included in her 
national identity-card (by assumption).
She will use \(k\) to compute \(pid\gets PRF_k(id)\), which is her anonymous 
identity during the protest.
She must also provide \iac{NIZK} proof that \(pid = PRF_k(id)\) and that she 
knows a signature by the identity authority on \(k\).
Thus \(pid\) will be used as the unique identifier in the proof shares (and all 
computations below) whereas the \ac{NIZK} proof will be used separately to prove 
the validity (eligibility) of \(pid\).

\subsubsection{Temporal eligibility, created after start}

Given the properties of the storage (in \cref{StorageProperties}), for 
\cref{CreatedAfterStart}, Alice and Bob must include the hash value of an 
existing block in the blockchain in each proof share (shown as \(t_s\) in 
\cref{ProofFig}).
Then it is clear that the proof must have been created after that block (since 
predicting such a value is hard).

@@

\subsubsection{Temporal eligibility, created before end}

Given the properties of the storage system in \cref{StorageProperties}, 
\cref{CreatedBeforeEnd} is straight-forward: Alice and Bob simply commit their 
proofs to the blockchain as soon as possible after they have participated in the 
protest.
Thus we can infer that a proof (or proof share) was created at the latest when 
it was committed.
